Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-17 manuscript/manuscript.Rmd
results

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations*.
For $n$ species, these models have the general form
\begin{align}
  \label{eq:general model}
  N_{t+1} - N_t = f(N_t) - h_t := N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, and $h_t$ is the harvest size at timestep $t$.

@@

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  X_{t+1} - X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t,
\end{align}
where,
\begin{align*}
  F(X,H;\ \beta,c) := \frac{\beta H X^2}{c^2 + X^2}.
\end{align*}
The model has five parameters: the growth rate $r$ and carrying capacity $K$ for $X$, a constant population $H$ of a species which preys on $X$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

@@

@@

>>>>

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations*.
For $n$ species, these models have the general form
\begin{align}
  \label{eq:general model}
  N_{t+1} - N_t = f(N_t) - h_t := \Delta N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, and $h_t$ is the harvest size at timestep $t$.

@@

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t,
\end{align}
where,
\begin{align*}
  F(X,H;\ \beta,c) := \frac{\beta H X^2}{c^2 + X^2}.
\end{align*}
The model has five parameters: the growth rate $r$ and carrying capacity $K$ for $X$, a constant population $H$ of a species which preys on $X$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

@@

## Stochastic dynamics

\textbf{Probably just merge on previous sections.}
We consider a stochastic contribution to the system's dynamics.
This way, eq. \eqref{eq:may} becomes
\begin{align}
  \label{eq:may stoch}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t + \eta_t,
\end{align}
where $\{\eta_t\}_t$ are independent Gaussian variables with zero mean.
The variance $\sigma^2$ of $\eta_t$ is an additional parameter of the model.

Similarly, eq. \eqref{eq:3d model} becomes
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}

@@

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information. 
The agent was trained using the PPO algorithm, using a neural network with two hidden layers of 64 neurons to express $\pi$.
Details of the training process may be found in App. \ref{app:tbd}.
Our code is available at TBD.
